Open-source landscape for 3D CSEM modelling

### 2020-05-18 manuscript/Manuscript.tex
Median Figure
- Integrate the figure into the comparison notebook.
- Combine the three plots into one plot, only one colorbar.
- Change the median calulation to only take the abs() once.

\begin{figure}
	\centering
	\includegraphics[width=5cm]{figures/median-stats-block--3.pdf}\hfill
	\includegraphics[width=5cm]{figures/median-stats-block-0.pdf}\hfill
	\includegraphics[width=5cm]{figures/median-stats-block-3.pdf}
	\caption[Median errors]{Overall misfit relations between all codes for the three receiver lines y=-3, y=0 \& y=3 f.l.t.r. Colors indicate the median values of the 101 calculated NRMSD arguments for each line between all codes. Errors for real parts are shown in the lower triangle, for imaginary parts in the upper triangle.}
	\label{medianmisfits}	
\end{figure}

>>>>

%
\plot*{median-stats-block}{width=\textwidth}{
    Overall misfit relations between all codes for the three receiver lines
    y=-3, y=0, and y=3 (f.l.t.r.). Colors indicate the median values of the 101
    calculated NRMSD arguments for each line between all codes. Errors for real
    parts are shown in the lower triangle, for imaginary parts in the upper
  triangle.
}
%
